---
title: "Calculate the solar elevation angles with R"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Calculate the solar elevation angles with R}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Solar altitude Angle is the Angle between the sun's rays at a place and the section of the earth's surface through which they pass to the center of the earth.With this package, you can easily calculate the sun altitude Angle.

## Calculate the solar elevation angles

According to the input date and the local latitude value, we can get the solar altitude angle at that time.

```{r }
library(Geography)

SolarAltitudeAngle("2021/3/21 12:00:00",36.05)

SolarAltitudeAngle("2021/6/22 12:00:00",36.05)

SolarAltitudeAngle("2021/9/23 12:00:00",36.05)

SolarAltitudeAngle("2021/12/22 12:00:00",36.05)
```
This function needs to pass two parameters: date and latitude. It should be noted that the date should be at least accurate to the hour (24-hour system), otherwise the correct result cannot be obtained.In addition, the latitude and the solar elevation angles are expressed by the angle system.

Let's take a look at a wrong demonstration
```{r }

SolarAltitudeAngle("2021/3/21",36.05)

```
The result of the above code running is negative, which is obviously wrong.

## The data set

This data set is the solar altitude angle at 12:00 noon in Lanzhou through the above function, which is not the real measured data.

```{r}
head(LanZhou)
tail(LanZhou)
```
